--- 
title: "`r knitr::current_input()`"
date: "`r paste('last updated', 
    format(lubridate::now(), '%H:%M, %d %B %Y'))`"
output: 
  pdf_document: 
    latex_engine: xelatex
toc: TRUE 
toc_depth:  1 
fontsize: 12pt 
geometry: margin=0.5in,top=0.25in 
---

##  Test if token is valid


SETUP ! (begin here)
- once auth.code is stored in Options() s/d not need to be here
* For Troubleshooting
*  HEAD shows what is being sent (see the simple error?)
*  httr::HEAD("https://www.googleapis.com/youtube/v3/playlists",
 							query= query,
 							config = config) 

REF : 
https://www.r-bloggers.com/2019/01/how-to-authenticate-using-oauth2-through-r-2/
```{r setup, include=FALSE		}
knitr::opts_chunk$set(echo = TRUE,
                      comment = "      ##",
                      error = TRUE,
                      collapse = TRUE)
load_all()
```


```{r Token, eval=FALSE   }
# R6 object
httr::Token

```

```{r caching}

# .httr-oauth 
file.exists(".httr-oauth")

# options("httr_oauth_cache" = TRUE) 
# was caching option ON?
getOption("httr_oauth_cache")

```

```{r valid}

```



# =========
## LEGACY
# =========

## Initialization,  need only do once.
## Set up the token, .httr-oauth

Endpoints
```{r endpoints}

# 1. Find OAuth settings for google:
#    https://developers.google.com/accounts/docs/OAuth2InstalledApp
httr::oauth_endpoints("google")

```
  - Register myapp with Google
  - Uncomment if want to see
```{r register}
# 2. Register an application at https://cloud.google.com/console#/project
#    Replace key and secret below (use ~/.R_environ)
#    NOTE:  google calls this key as "Client ID"
myapp <- httr::oauth_app("google",
  key  <- Sys.getenv("OAUTH2_ID"),
  secret  <- Sys.getenv("OAUTH2_SECRET")
)
myapp
```

## SCOPES, auth.code
  - Create .httr-oauth (binary) in project root.
  - Best to run in xiwi -T st  b/c need X11 for user to approve

Simplest Scope
```{r .httr-oauth}
auth.code <- httr::oauth2.0_token(
              endpoint = httr::oauth_endpoints("google"),
              app = myapp,
              scope = "https://www.googleapis.com/auth/userinfo.profile")

```

## Is auth.code valid?
See 011_httr_check_valid_token.Rmd


now use GET, Works
```{r use_api}
# 4. Use API (auto-refreshs a stale OAuth token)
req <- GET(
  "https://www.googleapis.com/oauth2/v1/userinfo",
  config(token = auth.code) )

stop_for_status(req)
str(content(req))

# show header
httr::HEAD(
  "https://www.googleapis.com/oauth2/v1/userinfo",
  config(token = auth.code) 
)
```

## SCOPE 2  
  - Need broader scope to access email
```{r get_email}
auth.code <- oauth2.0_token(
              endpoint = oauth_endpoints("google"),
              app = myapp,
         scope = c("https://www.googleapis.com/auth/userinfo.profile",
                "https://www.googleapis.com/auth/userinfo.email")
)

# same request (but token has changed!)
req <- GET(
  "https://www.googleapis.com/oauth2/v1/userinfo",
  config(token = auth.code) )

stop_for_status(req)
# email appears!
str(content(req))
```

##  SCOPE 3 (BEST)
  - USE THIS auth.code for most work
  - must be in X11  
  - Add scope for various youtube access.
  - youtube.force-ssl needed to retrieve user's playists, videos in each
```{r youtube_scopes}
# pop, asks users,  AND warns not verified, not safe
auth.code <- httr::oauth2.0_token(
              endpoint = httr::oauth_endpoints("google"),
              app = myapp,
         scope = c("https://www.googleapis.com/auth/userinfo.profile",
                "https://www.googleapis.com/auth/userinfo.email",
                "https://www.googleapis.com/auth/youtube",  # manage
"https://www.googleapis.com/auth/youtube.readonly",
"https://www.googleapis.com/auth/youtube.force-ssl"
         )
)

```

KEY STEP  ...  save auth.code
-  later retrieve getOption("auth.code")
-  NOTE:  auth.code should not be NULL

```{r save_auth.code}
auth.code
base::options("auth.code" = auth.code)
```


