--- 
title: Template for .Rmd 
date: "`r paste('last updated', 
    format(lubridate::now(), '%H:%M, %d %B %Y'))`"
output: 
  pdf_document: 
    latex_engine: xelatex
toc: TRUE 
toc_depth:  1 
fontsize: 12pt 
geometry: margin=0.5in,top=0.25in 
---


REMOVE??

REF : 
https://www.r-bloggers.com/2019/01/how-to-authenticate-using-oauth2-through-r-2/
```{r setup, include=FALSE		}
knitr::opts_chunk$set(echo = TRUE,
                      comment = "      ##",
                      error = TRUE,
                      collapse = TRUE)
load_all()
library(httr)
```

## Initialization,  need only do once.
## Set up the token, .httr-oauth

Endpoints
```{r endpoints}

# 1. Find OAuth settings for google:
#    https://developers.google.com/accounts/docs/OAuth2InstalledApp
oauth_endpoints("google")
```


  - Register myapp with Google
  - Uncomment if want to see
```{r register}
# 2. Register an application at https://cloud.google.com/console#/project
#    Replace key and secret below (use ~/.R_environ)
#    NOTE:  google calls this key as "Client ID"
myapp <- oauth_app("google",
  key  <- Sys.getenv("OAUTH2_ID"),
  secret  <- Sys.getenv("OAUTH2_SECRET")
)

# Sys.getenv("API_KEY")
# myapp
```
  - Create .httr-oauth (binary) in project root.
  - Best to run in xiwi -T st  b/c need X11 for user to approve

  - ONCE .httr_oauth created,  oauth2.0_token() will find it, refresh it and without needed X11 or user approval. 
```{r .httr-oauth}

# Simplest Scope here.
auth.code <- oauth2.0_token(
              endpoint = oauth_endpoints("google"),
              app = myapp,
              scope = "https://www.googleapis.com/auth/userinfo.profile")



```

now use GET, Works
```{r use_api}
# 4. Use API (auto-refreshs a stale OAuth token)
req <- GET(
  "https://www.googleapis.com/oauth2/v1/userinfo",
  config(token = auth.code) )

stop_for_status(req)
str(content(req))

# show header
httr::HEAD(
  "https://www.googleapis.com/oauth2/v1/userinfo",
  config(token = auth.code) 
)
```

  - Need broader scope to access email
```{r get_email}
auth.code <- oauth2.0_token(
              endpoint = oauth_endpoints("google"),
              app = myapp,
         scope = c("https://www.googleapis.com/auth/userinfo.profile",
                "https://www.googleapis.com/auth/userinfo.email")
)

# same request (but token has changed!)
req <- GET(
  "https://www.googleapis.com/oauth2/v1/userinfo",
  config(token = auth.code) )

stop_for_status(req)
# email appears!
str(content(req))
```

  - Add scope for various youtube access.
  - youtube.force-ssl needed to retrieve user's playists, videos in each
```{r youtube_scopes}
# pop, asks users,  AND warns not verified, not safe
auth.code <- oauth2.0_token(
              endpoint = oauth_endpoints("google"),
              app = myapp,
         scope = c("https://www.googleapis.com/auth/userinfo.profile",
                "https://www.googleapis.com/auth/userinfo.email",
                "https://www.googleapis.com/auth/youtube",  # manage
"https://www.googleapis.com/auth/youtube.readonly",
"https://www.googleapis.com/auth/youtube.force-ssl"
         )
)

```

```{r one_video}

# prep for GET
if (!exists("api")) api <- get_api_codes()

l <- get_typical_yt()
maxResults  <- l$maxResults
playlistId  <- l$playlistId
video_id = l$videoId
base_url <- "https://www.googleapis.com/youtube/v3/videos"


api_opts <- list(part = "snippet",
                 id = video_id,
                 maxResults = maxResults,
                 fields="items(snippet(title))",
                 key = api$api_key)


# what is this?
httr::modify_url(
                       base_url, 
                       query = api_opts, 
                       config(token = auth.code))

# WORKS!!!!
r  <- GET(base_url, query = api_opts, config(token= auth.code))
stop_for_status(r)
httr::content(r)
str(httr::content(r))
```

STOP HERE
more examples, see 00070 or other files

```{r knit_exit()} 
knitr::knit_exit()
```

/newpage

```{r render, eval=FALSE	} 
file <- ""
file  <- basename(file)
dir <- "rmd"

jimTools::ren_pdf(file,dir)
jimTools::ren_github(file, dir)
```
