---
title: Template for .Rmd
output: 
  pdf_document:
    latex_engine: xelatex
    toc:  TRUE
    toc_depth:  1
fontsize: 12pt
geometry: margin=0.5in,top=0.25in
#  md_document:
#  html_document:
#    toc: true
#  	toc_float: true
#    css: styles.css
---

```{r setup, include=FALSE		}
knitr::opts_chunk$set(echo = TRUE,  
											comment="      ##",  
											error=TRUE, collapse=TRUE)
```

```{r library, include=FALSE		}
library(jimTools)
library(here)
load_all()
```

```{r render, eval=FALSE	}
here()
file <- "/home/jim/code/r_rafael/rmd/005_linear_algebra_examples.Rmd"
file  <- basename(file)
dir="rmd"

jimTools::ren_pdf(file,dir)
jimTools::ren_github(file, dir)
```

Notes:
001_try_tuber_youtube_api.R
my Google credentials: https://console.cloud.google.com/apis/credentials?project=sunny-aleph-164504

References
youtube api:  https://developers.google.com/youtube/v3/getting-started

[google api explorer:]( https://developers.google.com/youtube/v3/docs/?apix=true)

R-bloggers example: https://www.r-bloggers.com/using-the-tuber-package-to-analyse-a-youtube-channel/ 
 tuber: https://soodoku.github.io/tuber/articles/tuber-ex.html


```{r get_api}
api <- get_api_codes()
```


001 get token and set .httr_oauth (if not done before)
```{r oauth2}
tuber::yt_oauth(
app_id = api$oauth2_id,
app_secret = api$oauth2_secret
)
```


***
CLEAN UP!

```{r}

# some samples:

#channel_id <- "UClB5qWyXejlAwwkDAzJis-Q" # my channel
#video_id <- "UCVdHFHpFBg"   # Tex Ritter Range Party
video_id <- "UCVdHFHpFBg"   # Tex Ritter Range Party
a <- tuber::get_stats(video_id=video_id)

x <- tibble::as_tibble(a)   # works
x
# but
y <- tibble(a)   #  leaves as list

details <- tuber::get_video_details(video_id = video_id )
d <- as_tibble(details)
```


05_channel_all_playlists
```{r}
get_playlists(
    filter=c(channel_id="UClB5qWyXejlAwwkDAzJis-Q"),
    part="snippet,contentDetails",
    max_results = 10,
    simplify=TRUE,
    fields="items(id,snippet(title,position))"
)

```

#### 06_list_channel_videos (ID only?)
```{r}

# my channel_id=UClB5qWyXejlAwwkDAzJis-Q
channel_id <- "UClB5qWyXejlAwwkDAzJis-Q" # mine
channel_id <- "UCT5Cx1l4IS3wHkJXNyuj4TA"
z<-list_channel_videos(channel_id=channel_id,
                       max_results = 4  )
z<-list_channel_videos(max_results = 4, mine=TRUE  )
z
```

#### channel, pick playlist, show videos
```{r}
filter=c(channel_id="UClB5qWyXejlAwwkDAzJis-Q")


# choose ONE
## my channel
#channel_id <- "UClB5qWyXejlAwwkDAzJis-Q"

# code example
channel_id <- "UCT5Cx1l4IS3wHkJXNyuj4TA"



a <- list_channel_resources(filter =  c(channel_id=channel_id),
                            part="contentDetails")

# 
playlist_id <- a$items[[1]]$contentDetails$relatedPlaylists$uploads

# Get videos on the playlist, data.frame
vids <- get_playlist_items(filter= c(playlist_id=playlist_id)) 


# as vector
# Video ids
vid_ids <- as.vector(vids$contentDetails.videoId)

# Function to scrape stats for all vids
get_all_stats <- function(id) {
  get_stats(id)
} 

# returns list
res <- map(vid_ids, get_all_stats)

as_tibble(res)
```

#### playlist
```{r}
get_stats(video_id="N708P-A45D0")

# "toDownload"
t <- tibble(get_playlist_items(
    filter = c(playlist_id ="PLbcglKxZP5PMDe2rhvTaahCV3BzFurnYJ"),
    part="contentDetails",
    simplify = TRUE) # return df
)
t %>% head(kind)
glimpse(t)
```

#### yt_search .... baffled how works
```{r}
# my channel?   UClB5qWyXejlAwwkDAzJis-Q
# = Channel stats = #
chstat = get_channel_stats("UClB5qWyXejlAwwkDAzJis-Q")

# = Videos = #
videos = yt_search(term="", type="video", channel_id = "UClB5qWyXejlAwwkDAzJis-Q")

videos = videos %>%
  mutate(date = as.Date(publishedAt)) %>%
  arrange(date)

```


Works
try short playlist
```{r}
# koreader (2 videos)
#list=PLbcglKxZP5PNQf6pOEfQ7LNsGSvSULa1a

v <- get_playlist_items(filter = c(playlist_id="PLbcglKxZP5PNQf6pOEfQ7LNsGSvSULa1a"), 
                        part="snippet",
                   max_results = 51)
t <- as_tibble(v)

glimpse(t)
t %>% select(snippet.title, snippet.publishedAt) %>% knitr::kable()
```


Longer  playlist
```{r}
# calm down playlist    
list="PLBBABD9C8CA13B2F5" (Works)
# R playist(44)
PLbcglKxZP5PMSKRxgVtFG2yrYhcCFgSJU

# v is list 
v <- get_playlist_items(filter = 
   c(playlist_id="PLBBABD9C8CA13B2F5"), 
                        part="snippet",
                   max_results = 2000)
eval(list)
t <- as_tibble(v)
t %>% select(snippet.title, snippet.publishedAt) %>% knitr::kable()
```

#### list all playlist titles
```{r}

# max playlists =50 
z <- tibble(get_playlists(
    filter=c(channel_id="UClB5qWyXejlAwwkDAzJis-Q"),
    part="snippet,contentDetails",
    max_results = 50,
    simplify=TRUE)
)


# remove layers 
l <- z[[1]][[5]]

# l holds all playlists 
length(l)

# number of snips is number of playlist s
snips <- map(l, "snippet")

map_chr(snips, "title")
```




```{r knit_exit()}
knitr::knit_exit()
```

***





CLEAN UP

sets .httr_oauth (unless exists)
returns token
[yt_oauth.R](https://github.com/soodoku/tuber/blob/master/R/yt_oauth.R)
```{r how_yt_oauth_works, eval=FALSE, include = FALSE	 }

tuber::yt_oauth(app_id = NULL, 
  app_secret = NULL, 
	scope = "ssl",
  token = ".httr-oauth", ...)

If .httr-oauth 
*	EXISTS, reads it, assigns to google-token
* NOT EXIST, 
	(1)   myapp <- oauth_app("google", key = app_id, secret =
	app_secret)
	(2)   gets token (assuming default scope: ssl)
	google_token <- oauth2.0_token(
	  oauth_endpoints("google"), 
		myapp,
    scope = "https://www.googleapis.com/auth/youtube.force-ssl", ...)
	(2a) also, this httr function also caches token to file:  .httr-oauth
	(3)  stores token in option:  
	options(google_token = google_token)

	validate_oauth2.0() is actual call to Google

```
