---
title: Template for .Rmd
output: 
  pdf_document:
    latex_engine: xelatex
    toc:  TRUE
    toc_depth:  1
fontsize: 12pt
geometry: margin=0.5in,top=0.25in
#  md_document:
#  html_document:
#    toc: true
#  	toc_float: true
#    css: styles.css
---

/home/jim/code/pkg_yt_api/exclude/011_playlists.Rmd

---- PURPOSE ----
given a , return list of all playlists
----------------
```{r setup, include=FALSE		}
knitr::opts_chunk$set(echo = TRUE,  
											comment="      ##",  
											error=TRUE, 
											collapse=TRUE)
```

```{r library, include=FALSE		}
library(jimTools)
library(here)
library(dplyr)
library(magrittr)
load_all()
```
```{r render, eval=FALSE	}
here()
file <- "/home/jim/code/r_rafael/rmd/005_linear_algebra_examples.Rmd"
file  <- basename(file)
dir="rmd"

jimTools::ren_pdf(file,dir)
jimTools::ren_github(file, dir)
```
 ---- set once ----
```{r token}
api <- get_api_codes()
myapp  <- tuber::yt_oauth(app_id = api$oauth2_id,
													app_secret = api$oauth2_secret
)
```
```{r initialize}
l <- get_typical_yt()
base_url <- "https://www.googleapis.com/youtube/v3/playlists"

```

```{r query}

query  <- set_query( 
					part="snippet",
					channelId = l$channelId,
					maxResults = l$maxResults,
         fields="nextPageToken,items(id,snippet(title,description,channelId,publishedAt))",
					key = api$api_key,
					pageToken = NULL)
```

```{r call }
r <- httr::GET(base_url, 
           query = query,
					 config = httr::config(token=getOption("google_token"))) %>% 
						 httr::stop_for_status()
)
json_content <- get_json(r)

# playlists is data.frame, 50 x 4
playlists <- json_content$items$snippet

##  sTART HERE
##more batches ?
# ---- loop till no more token ---

while ( !is.null(get_nextPageToken(r)) ) {

# only 1 change
pageToken <- get_nextPageToken(r)

query  <- set_query( part="snippet",
							maxResults =maxResults,
							mine = TRUE,
              fields="nextPageToken,items(id,snippet(title,description,channelId,publishedAt))",
							key = api$api_key,
							pageToken = pageToken)


config  <- set_config(token = google_token)

r <- httr::GET(base_url, 
               query = query,
               config = config 
               )


json_content <- get_json(r)
# claim:   playlists is data.frame, 50 x 2
next_playlists <- json_content$items$snippet
playlists <- rbind(playlists, next_playlists)
}
playlists
##

# google stores dates as ISO 8601, as string
# why need TWO lubridate commands to retrieve simple date?
playlists <- playlists %>% 
	dplyr::mutate(date= lubridate::as_date(
									lubridate::as_datetime(publishedAt))) %>% 
	dplyr::select(-c(channelId,publishedAt))

playlists


